Measurement of deeply virtual Compton scattering off Helium-4 with CLAS at Jefferson Lab

### 2020-04-22 eg6-letters/long-paper/prc-dvcshelium.tex
Small addition to summary

We report the measurement of the coherent and incoherent DVCS processes off helium-4 with
CLAS at JLab. To properly isolate the coherent channel, the experiment used a specially 
designed RTPC to detect the scattered helium-4. While statistically limited, this coherent 
DVCS measurement reveals the large BSA ($\sim 35$\%) expected by theoretical calculations
made in the impulse approximation. Moreover, we showed that the CFF extraction can be 
immediately performed using these data without any model prescription. The incoherent DVCS measurement 
however reveals relatively small asymmetries in comparison to previous free proton 
measurements. It remains unclear what is the source of the suppression of the BSA as both 
initial and final state effect contributions could lead to such outcome.

@@

% \begin{figure}
% \includegraphics{}%
% \caption{\label{}}
% \end{figure}

% Surround figure environment with turnpage environment for landscape
% figure
% \begin{turnpage}
% \begin{figure}
% \includegraphics{}%
% \caption{\label{}}
% \end{figure}
% \end{turnpage}

% tables should appear as floats within the text
%
% Here is an example of the general form of a table:
% Fill in the caption in the braces of the \caption{} command. Put the label
% that you will use with \ref{} command in the braces of the \label{} command.
% Insert the column specifiers (l, r, c, d, etc.) in the empty braces of the
% \begin{tabular}{} command.
% The ruledtabular enviroment adds doubled rules to table and sets a
% reasonable default table settings.
% Use the table* environment to get a full-width table in two-column
% Add \usepackage{longtable} and the longtable (or longtable*}
% environment for nicely formatted long tables. Or use the the [H]
% placement option to break a long table (with less control than 
% in longtable).
% \begin{table}%[H] add [H] placement to break table across pages
% \caption{\label{}}
% \begin{ruledtabular}
% \begin{tabular}{}
% Lines of table here ending with \\
% \end{tabular}
% \end{ruledtabular}
% \end{table}

% Specify following sections are appendices. Use \appendix* if there
% only one appendix.
%\appendix
%\section{}

% Surround table environment with turnpage environment for landscape
% table
% \begin{turnpage}
% \begin{table}
% \caption{\label{}}
% \begin{ruledtabular}
% \begin{tabular}{}
% \end{tabular}
% \end{ruledtabular}
% \end{table}
% \end{turnpage}

@@

\section{Table of results with information on full kinematics}
\label{sec:fullresults}
 tests

>>>>

We report the measurement of the coherent and incoherent DVCS processes off helium-4 with
CLAS at JLab. To properly isolate the coherent channel, the experiment used a specially 
designed RTPC to detect the scattered helium-4. This coherent 
DVCS measurement reveals the large BSA ($\sim 35$\%) expected by theoretical calculations
made in the impulse approximation. Moreover, we showed that the CFF extraction can be 
immediately performed using these data without any model prescription. The incoherent DVCS measurement 
however reveals relatively small asymmetries in comparison to previous free proton 
measurements. It remains unclear what is the source of the suppression of the BSA as both 
initial and final state effect contributions could lead to such outcome. We presented 
various models for both channels, while old and recent work agree nicely with the data
from the coherent channel, it appears more difficult to reproduce the incoherent ones.
A future experimental program using tagging at the upgraded CLAS12 detector is 
planned to address this question in the coming years by using a new recoil detector 
design~\cite{Armstrong:2017zcm}.

@@

@@

\section{Table of results with kinematic information}
\label{sec:fullresults}

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
         \hline
  1.143 & 0.136 & 0.096 & 24.3  &  0.1327 $\pm$ 0.1088 $\pm$ 0.0257 \\ 
  1.143 & 0.136 & 0.096 & 61.1  &  0.3210 $\pm$ 0.0932 $\pm$ 0.0188 \\ 
  1.143 & 0.136 & 0.096 & 98.9  &  0.3709 $\pm$ 0.1026 $\pm$ 0.0403 \\ 
  1.143 & 0.136 & 0.096 & 140.9 &  0.2452 $\pm$ 0.1517 $\pm$ 0.0267 \\ 
  1.143 & 0.136 & 0.096 & 178.4 &  0.0225 $\pm$ 0.1632 $\pm$ 0.0278 \\ 
  1.143 & 0.136 & 0.096 & 219.1 & -0.0526 $\pm$ 0.1475 $\pm$ 0.0248 \\ 
  1.143 & 0.136 & 0.096 & 262.9 & -0.2642 $\pm$ 0.1196 $\pm$ 0.0389 \\ 
  1.143 & 0.136 & 0.096 & 301.9 & -0.1761 $\pm$ 0.0968 $\pm$ 0.0263 \\ 
  1.143 & 0.136 & 0.096 & 337.7 & -0.2791 $\pm$ 0.1047 $\pm$ 0.0343 \\ 
  \hline                                                                                                           
  1.423 & 0.172 & 0.099 & 21.1  &  0.1917 $\pm$ 0.0892 $\pm$ 0.0267 \\ 
  1.423 & 0.172 & 0.099 & 56.6  &  0.2819 $\pm$ 0.0866 $\pm$ 0.0250 \\ 
  1.423 & 0.172 & 0.099 & 96.9  &  0.4855 $\pm$ 0.1291 $\pm$ 0.0426 \\ 
  1.423 & 0.172 & 0.099 & 139.9 &  0.0996 $\pm$ 0.1679 $\pm$ 0.0250 \\ 
  1.423 & 0.172 & 0.099 & 180.3 &  0.1458 $\pm$ 0.1906 $\pm$ 0.0302 \\ 
  1.423 & 0.172 & 0.099 & 218.7 & -0.1109 $\pm$ 0.1853 $\pm$ 0.0344 \\ 
  1.423 & 0.172 & 0.099 & 263.1 & -0.3516 $\pm$ 0.1371 $\pm$ 0.0366 \\ 
  1.423 & 0.172 & 0.099 & 302.2 & -0.4141 $\pm$ 0.0842 $\pm$ 0.0383 \\ 
  1.423 & 0.172 & 0.099 & 338.2 & -0.2786 $\pm$ 0.0836 $\pm$ 0.0261 \\ 
  \hline                                                                                                           
  1.902 & 0.224 & 0.107 & 21.4  &  0.1803 $\pm$ 0.0805 $\pm$ 0.0234 \\ 
  1.902 & 0.224 & 0.107 & 57.2  &  0.3501 $\pm$ 0.0824 $\pm$ 0.0185 \\ 
  1.902 & 0.224 & 0.107 & 96.2  &  0.2701 $\pm$ 0.1230 $\pm$ 0.0173 \\ 
  1.902 & 0.224 & 0.107 & 139.5 &  0.3053 $\pm$ 0.2390 $\pm$ 0.0170 \\ 
  1.902 & 0.224 & 0.107 & 178.2 &  0.1028 $\pm$ 0.2670 $\pm$ 0.0126 \\ 
  1.902 & 0.224 & 0.107 & 221.4 & -0.2118 $\pm$ 0.2147 $\pm$ 0.0152 \\ 
  1.902 & 0.224 & 0.107 & 263.3 & -0.3060 $\pm$ 0.1306 $\pm$ 0.0260 \\ 
  1.902 & 0.224 & 0.107 & 303.3 & -0.1384 $\pm$ 0.0944 $\pm$ 0.0207 \\ 
  1.902 & 0.224 & 0.107 & 338.5 & -0.1633 $\pm$ 0.0791 $\pm$ 0.0163 \\ 
         \hline \hline
      \end{tabular}
      \caption{Values of the coherent $A_{LU}$ in $Q^2$ bins from Fig. \ref{fig:CohALUphi}.}
      \label{table:Coh_Q2_BSA}
   \end{center}
\end{table}

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
         \hline

  1.164 & 0.132 & 0.095 & 25.6  &  0.0174 $\pm$ 0.1440 $\pm$ 0.0221 \\
  1.164 & 0.132 & 0.095 & 61.6  &  0.3478 $\pm$ 0.0867 $\pm$ 0.0198 \\
  1.164 & 0.132 & 0.095 & 99.0  &  0.3808 $\pm$ 0.0948 $\pm$ 0.0408 \\
  1.164 & 0.132 & 0.095 & 141.7 &  0.2943 $\pm$ 0.1379 $\pm$ 0.0333 \\
  1.164 & 0.132 & 0.095 & 178.1 &  0.0433 $\pm$ 0.1519 $\pm$ 0.0293 \\
  1.164 & 0.132 & 0.095 & 218.5 & -0.0352 $\pm$ 0.1316 $\pm$ 0.0243 \\
  1.164 & 0.132 & 0.095 & 262.7 & -0.2771 $\pm$ 0.1050 $\pm$ 0.0372 \\
  1.164 & 0.132 & 0.095 & 300.7 & -0.2138 $\pm$ 0.0836 $\pm$ 0.0259 \\
  1.164 & 0.132 & 0.095 & 335.2 & -0.2339 $\pm$ 0.1221 $\pm$ 0.0319 \\
   \hline                                                                                                         
  1.439 & 0.17 & 0.099 &  22.9  &  0.1579 $\pm$ 0.0853 $\pm$ 0.0230 \\
  1.439 & 0.17 & 0.099 &  57.1  &  0.1733 $\pm$ 0.0880 $\pm$ 0.0195 \\
  1.439 & 0.17 & 0.099 &  96.3  &  0.2259 $\pm$ 0.1331 $\pm$ 0.0295 \\
  1.439 & 0.17 & 0.099 &  139.1 &  0.2454 $\pm$ 0.1758 $\pm$ 0.0187 \\
  1.439 & 0.17 & 0.099 &  180.1 & -0.1021 $\pm$ 0.1918 $\pm$ 0.0197 \\
  1.439 & 0.17 & 0.099 &  218.9 & -0.2876 $\pm$ 0.1909 $\pm$ 0.0270 \\
  1.439 & 0.17 & 0.099 &  263.9 & -0.2943 $\pm$ 0.1360 $\pm$ 0.0292 \\
  1.439 & 0.17 & 0.099 &  302.5 & -0.3979 $\pm$ 0.0921 $\pm$ 0.0331 \\
  1.439 & 0.17 & 0.099 &  338.1 & -0.2692 $\pm$ 0.0834 $\pm$ 0.0254 \\
   \hline                                                                                                         
  1.844 & 0.225 & 0.107 & 20.1  &  0.2626 $\pm$ 0.0755 $\pm$ 0.0248 \\
  1.844 & 0.225 & 0.107 & 55.9  &  0.4281 $\pm$ 0.0887 $\pm$ 0.0224 \\
  1.844 & 0.225 & 0.107 & 96.4  &  0.4925 $\pm$ 0.1390 $\pm$ 0.0271 \\
  1.844 & 0.225 & 0.107 & 137.7 & -0.2736 $\pm$ 0.2804 $\pm$ 0.0166 \\
  1.844 & 0.225 & 0.107 & 179.8 &  0.8470 $\pm$ 0.2497 $\pm$ 0.0204 \\
  1.844 & 0.225 & 0.107 & 224.7 & -0.0513 $\pm$ 0.2811 $\pm$ 0.0270 \\
  1.844 & 0.225 & 0.107 & 262.8 & -0.3416 $\pm$ 0.1694 $\pm$ 0.0353 \\
  1.844 & 0.225 & 0.107 & 304.5 & -0.1359 $\pm$ 0.1025 $\pm$ 0.0263 \\
  1.844 & 0.225 & 0.107 & 339.8 & -0.1658 $\pm$ 0.0770 $\pm$ 0.0175 \\

         \hline 
         \hline
      \end{tabular}
      \caption{Values of the coherent $A_{LU}$ in $x_B$ bins from Fig. \ref{fig:CohALUphi}.}
      \label{table:Coh_xB_BSA}
   \end{center}
\end{table}

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
  \hline
  1.36 & 0.160 & 0.080  & 22.8  &  0.2378 $\pm$ 0.0928 $\pm$ 0.0263 \\
  1.36 & 0.160 & 0.080  & 57.6  &  0.3014 $\pm$ 0.0874 $\pm$ 0.0243 \\
  1.36 & 0.160 & 0.080  & 98.1  &  0.4896 $\pm$ 0.1118 $\pm$ 0.0394 \\
  1.36 & 0.160 & 0.080  & 139.3 &  0.1965 $\pm$ 0.1595 $\pm$ 0.0252 \\
  1.36 & 0.160 & 0.080  & 178.8 &  0.0577 $\pm$ 0.1923 $\pm$ 0.0371 \\
  1.36 & 0.160 & 0.080  & 222.6 & -0.1651 $\pm$ 0.1640 $\pm$ 0.0370 \\
  1.36 & 0.160 & 0.080  & 265.6 & -0.3467 $\pm$ 0.1339 $\pm$ 0.0403 \\
  1.36 & 0.160 & 0.080  & 300.0 & -0.2891 $\pm$ 0.0928 $\pm$ 0.0294 \\
  1.36 & 0.160 & 0.080  & 339.3 & -0.1849 $\pm$ 0.0856 $\pm$ 0.0281 \\
  \hline                                                                
  1.507 & 0.179 & 0.094 & 21.1  &  0.2481 $\pm$ 0.0931 $\pm$ 0.0267 \\ 
  1.507 & 0.179 & 0.094 & 56.4  &  0.3386 $\pm$ 0.0828 $\pm$ 0.0284 \\ 
  1.507 & 0.179 & 0.094 & 97.5  &  0.3467 $\pm$ 0.1156 $\pm$ 0.0307 \\ 
  1.507 & 0.179 & 0.094 & 141.9 &  0.1464 $\pm$ 0.1887 $\pm$ 0.0215 \\ 
  1.507 & 0.179 & 0.094 & 179.5 & -0.2814 $\pm$ 0.1864 $\pm$ 0.0360 \\ 
  1.507 & 0.179 & 0.094 & 218.5 &  0.2104 $\pm$ 0.1998 $\pm$ 0.0147 \\ 
  1.507 & 0.179 & 0.094 & 262.8 & -0.2399 $\pm$ 0.1280 $\pm$ 0.0283 \\ 
  1.507 & 0.179 & 0.094 & 303.5 & -0.1989 $\pm$ 0.0955 $\pm$ 0.0286 \\ 
  1.507 & 0.179 & 0.094 & 338.5 & -0.2098 $\pm$ 0.0875 $\pm$ 0.0201 \\ 
  \hline                                                                                                                 
  1.610 & 0.193 & 0.127 & 22.3  &  0.0280 $\pm$ 0.0909 $\pm$ 0.0214 \\
  1.610 & 0.193 & 0.127 & 60.7  &  0.3582 $\pm$ 0.0932 $\pm$ 0.0204 \\
  1.610 & 0.193 & 0.127 & 96.8  &  0.2559 $\pm$ 0.1269 $\pm$ 0.0313 \\
  1.610 & 0.193 & 0.127 & 139.9 &  0.2207 $\pm$ 0.1930 $\pm$ 0.0203 \\
  1.610 & 0.193 & 0.127 & 178.5 &  0.5138 $\pm$ 0.1832 $\pm$ 0.0354 \\
  1.610 & 0.193 & 0.127 & 217.5 & -0.2473 $\pm$ 0.1664 $\pm$ 0.0189 \\
  1.610 & 0.193 & 0.127 & 260.9 & -0.2919 $\pm$ 0.1295 $\pm$ 0.0327 \\
  1.610 & 0.193 & 0.127 & 303.4 & -0.2488 $\pm$ 0.0892 $\pm$ 0.0280 \\
  1.610 & 0.193 & 0.127 & 336.8 & -0.2825 $\pm$ 0.0901 $\pm$ 0.0261 \\
         \hline
         \hline
      \end{tabular}
      \caption{Values of the coherent $A_{LU}$ in $-t$ bins from Fig. \ref{fig:CohALUphi}.}
      \label{table:Coh_t_BSA}
   \end{center}
\end{table}

% incoherent channel

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
 \hline 
  1.404 & 0.166 & 0.376  &   21.0 &   0.0541 $\pm$  0.0442  $\pm$ 0.0120 \\
  1.404 & 0.166 & 0.376  &   62.9 &   0.0771 $\pm$  0.0461  $\pm$ 0.0156 \\
  1.404 & 0.166 & 0.376  &   95.4 &   0.1913 $\pm$  0.0472  $\pm$ 0.0263 \\
  1.404 & 0.166 & 0.376  &  140.1 &   0.1076 $\pm$  0.0561  $\pm$ 0.0158 \\
  1.404 & 0.166 & 0.376  &  182.3 &   0.0448 $\pm$  0.0693  $\pm$ 0.0234 \\
  1.404 & 0.166 & 0.376  &  220.4 &  -0.0294 $\pm$  0.0675  $\pm$ 0.0150 \\
  1.404 & 0.166 & 0.376  &  258.4 &  -0.1261 $\pm$  0.0459  $\pm$ 0.0226 \\
  1.404 & 0.166 & 0.376  &  303.1 &  -0.1238 $\pm$  0.0401  $\pm$ 0.0196 \\
  1.404 & 0.166 & 0.376  &  337.4 &  -0.0122 $\pm$  0.0537  $\pm$ 0.0142 \\
  \hline                                                              
  1.889 & 0.232 & 0.415  &   20.3 &   0.0143 $\pm$  0.0355  $\pm$ 0.0124 \\
  1.889 & 0.232 & 0.415  &   60.5 &   0.0668 $\pm$  0.0464  $\pm$ 0.0169 \\
  1.889 & 0.232 & 0.415  &   95.8 &   0.1297 $\pm$  0.0521  $\pm$ 0.0202 \\
  1.889 & 0.232 & 0.415  &  140.9 &   0.1651 $\pm$  0.0771  $\pm$ 0.0285 \\
  1.889 & 0.232 & 0.415  &  179.7 &   0.1589 $\pm$  0.0894  $\pm$ 0.0146 \\
  1.889 & 0.232 & 0.415  &  221.5 &  -0.2594 $\pm$  0.0808  $\pm$ 0.0430 \\
  1.889 & 0.232 & 0.415  &  260.3 &  -0.1280 $\pm$  0.0559  $\pm$ 0.0180 \\
  1.889 & 0.232 & 0.415  &  303.5 &  -0.1762 $\pm$  0.0386  $\pm$ 0.0198 \\
  1.889 & 0.232 & 0.415  &  338.2 &  -0.0303 $\pm$  0.0447  $\pm$ 0.0113 \\
  \hline                                                              
  2.339 & 0.288 & 0.497  &  20.8  &  0.0740  $\pm$  0.0330  $\pm$ 0.0135 \\
  2.339 & 0.288 & 0.497  &  58.2  &  0.1359  $\pm$  0.0458  $\pm$ 0.0101 \\
  2.339 & 0.288 & 0.497  &  94.7  &  0.1836  $\pm$  0.0567  $\pm$ 0.0176 \\
  2.339 & 0.288 & 0.497  & 140.9  & -0.0178  $\pm$  0.1008  $\pm$ 0.0161 \\
  2.339 & 0.288 & 0.497  & 181.8  &  0.0922  $\pm$  0.1329  $\pm$ 0.0236 \\
  2.339 & 0.288 & 0.497  & 225.0  & -0.0751  $\pm$  0.1066  $\pm$ 0.0212 \\
  2.339 & 0.288 & 0.497  & 261.0  & -0.2439  $\pm$  0.0596  $\pm$ 0.0241 \\
  2.339 & 0.288 & 0.497  & 303.0  & -0.1977  $\pm$  0.0384  $\pm$ 0.0153 \\
  2.339 & 0.288 & 0.497  & 338.7  & -0.0889  $\pm$  0.0397  $\pm$ 0.0145 \\
  \hline                                                              
  3.098 & 0.379 & 0.641  & 20.1   & 0.0959   $\pm$  0.0305  $\pm$ 0.0147 \\ 
  3.098 & 0.379 & 0.641  & 57.1   & 0.0817   $\pm$  0.0478  $\pm$ 0.0147 \\
  3.098 & 0.379 & 0.641  & 94.2   & 0.1632   $\pm$  0.0684  $\pm$ 0.0281 \\
  3.098 & 0.379 & 0.641  &137.7   & 0.0930   $\pm$  0.1412  $\pm$ 0.0129 \\
  3.098 & 0.379 & 0.641  &180.2   &-0.2272   $\pm$  0.1918  $\pm$ 0.0270 \\
  3.098 & 0.379 & 0.641  &226.0   &-0.0333   $\pm$  0.1599  $\pm$ 0.0273 \\
  3.098 & 0.379 & 0.641  &263.9   &-0.1630   $\pm$  0.0802  $\pm$ 0.0214 \\
  3.098 & 0.379 & 0.641  &303.2   &-0.1644   $\pm$  0.0405  $\pm$ 0.0221 \\
  3.098 & 0.379 & 0.641  &340.5   &-0.0914   $\pm$  0.0368  $\pm$ 0.0141 \\
 \hline
 \hline
      \end{tabular}
      \caption{Values of the incoherent $A_{LU}$ in $Q^2$ bins from Fig. \ref{fig:InCohALUphi}.}
      \label{table:InCoh_Q2_BSA}
   \end{center}
\end{table}

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
         \hline
 1.449 & 0.163 & 0.374 &  21.0  &  0.0935 $\pm$ 0.0463  $\pm$  0.0137 \\ 
  1.449 & 0.163 & 0.374 &  63.4  &  0.0690 $\pm$ 0.0442  $\pm$  0.0165 \\ 
  1.449 & 0.163 & 0.374 &  95.6  &  0.1469 $\pm$ 0.0439  $\pm$  0.0216 \\ 
  1.449 & 0.163 & 0.374 & 140.3  &  0.1017 $\pm$ 0.0519  $\pm$  0.0149 \\ 
  1.449 & 0.163 & 0.374 & 181.3  &  0.0707 $\pm$ 0.0619  $\pm$  0.0235 \\ 
  1.449 & 0.163 & 0.374 & 220.0  & -0.0446 $\pm$ 0.0616  $\pm$  0.0199 \\ 
  1.449 & 0.163 & 0.374 & 258.5  & -0.1145 $\pm$ 0.0433  $\pm$  0.0183 \\ 
  1.449 & 0.163 & 0.374 & 303.0  & -0.0977 $\pm$ 0.0394  $\pm$  0.0154 \\ 
  1.449 & 0.163 & 0.374 & 336.9  &  0.0329 $\pm$ 0.0565  $\pm$  0.0105 \\ 
  \hline
  1.929 & 0.225 & 0.381 &  21.5  &  0.0016 $\pm$ 0.0383  $\pm$  0.0131 \\
  1.929 & 0.225 & 0.381 &  60.3  &  0.0556 $\pm$ 0.0441  $\pm$  0.0161 \\
  1.929 & 0.225 & 0.381 &  96.0  &  0.1681 $\pm$ 0.0495  $\pm$  0.0183 \\
  1.929 & 0.225 & 0.381 & 141.2  &  0.1422 $\pm$ 0.0788  $\pm$  0.0246 \\
  1.929 & 0.225 & 0.381 & 181.5  &  0.1672 $\pm$ 0.0957  $\pm$  0.0165 \\
  1.929 & 0.225 & 0.381 & 223.1  & -0.2619 $\pm$ 0.0828  $\pm$  0.0343 \\
  1.929 & 0.225 & 0.381 & 260.2  & -0.1845 $\pm$ 0.0517  $\pm$  0.0227 \\
  1.929 & 0.225 & 0.381 & 303.0  & -0.1962 $\pm$ 0.0367  $\pm$  0.0206 \\
  1.929 & 0.225 & 0.381 & 336.8  & -0.0410 $\pm$ 0.0455  $\pm$  0.0100 \\
  \hline
  2.334 & 0.283 & 0.468 &  20.9  &  0.0687 $\pm$ 0.0327  $\pm$  0.0198 \\
  2.334 & 0.283 & 0.468 &  59.2  &  0.1242 $\pm$ 0.0456  $\pm$  0.0195 \\
  2.334 & 0.283 & 0.468 &  94.1  &  0.1648 $\pm$ 0.0583  $\pm$  0.0188 \\
  2.334 & 0.283 & 0.468 & 139.3  &  0.1118 $\pm$ 0.1102  $\pm$  0.0242 \\
  2.334 & 0.283 & 0.468 & 180.7  & -0.1943 $\pm$ 0.1545  $\pm$  0.0145 \\
  2.334 & 0.283 & 0.468 & 225.2  &  0.0081 $\pm$ 0.1109  $\pm$  0.0140 \\
  2.334 & 0.283 & 0.468 & 261.4  & -0.2416 $\pm$ 0.0660  $\pm$  0.0272 \\
  2.334 & 0.283 & 0.468 & 303.3  & -0.1712 $\pm$ 0.0375  $\pm$  0.0178 \\
  2.334 & 0.283 & 0.468 & 338.4  & -0.0649 $\pm$ 0.0406  $\pm$  0.0101 \\
  \hline
  2.975 & 0.389 & 0.688 &   19.6 &   0.0809$\pm$  0.0289 $\pm$  0.0143 \\
  2.975 & 0.389 & 0.688 &   55.1 &   0.1214$\pm$  0.0539 $\pm$  0.0148 \\
  2.975 & 0.389 & 0.688 &   93.4 &   0.2530$\pm$  0.0899 $\pm$  0.0313 \\
  2.975 & 0.389 & 0.688 &  135.1 &  -0.2304$\pm$  0.2247 $\pm$  0.0386 \\
  2.975 & 0.389 & 0.688 &  179.9 &  -0.0522$\pm$  0.4248 $\pm$  0.0364 \\
  2.975 & 0.389 & 0.688 &  230.5 &  -0.3766$\pm$  0.3336 $\pm$  0.0469 \\
  2.975 & 0.389 & 0.688 &  265.5 &  -0.0929$\pm$  0.1030 $\pm$  0.0202 \\
  2.975 & 0.389 & 0.688 &  303.4 &  -0.1977$\pm$  0.0453 $\pm$  0.0229 \\
  2.975 & 0.389 & 0.688 &  341.2 &  -0.1084$\pm$  0.0352 $\pm$  0.0156 \\
 \hline
 \hline
 \end{tabular}
 \caption{Values of the incoherent $A_{LU}$ in $x_B$ bins from Fig. \ref{fig:InCohALUphi}.}
 \label{table:InCoh_xB_BSA}
 \end{center}
\end{table}

\begin{table}[!h]
   \begin{center}
      \begin{tabular}{||l|l|l|l|l||}
         \hline
 $<Q^{2}>$ & $<x_{B}>$ & $<-t>$ & $<\phi>$ & $A_{LU}$ $\pm$ stat. $\pm$ syst.\\
  \hline
  1.842 & 0.215 & 0.135  &   21.6  &  0.1197  $\pm$  0.0369 $\pm$ 0.0135 \\ 
  1.842 & 0.215 & 0.135  &   60.6  &  0.0273  $\pm$  0.0416 $\pm$ 0.0190 \\ 
  1.842 & 0.215 & 0.135  &   96.3  &  0.2189  $\pm$  0.0409 $\pm$ 0.0179 \\ 
  1.842 & 0.215 & 0.135  &  141.9  &  0.1502  $\pm$  0.0542 $\pm$ 0.0263 \\ 
  1.842 & 0.215 & 0.135  &  179.8  &  0.0083  $\pm$  0.0670 $\pm$ 0.0150 \\ 
  1.842 & 0.215 & 0.135  &  220.7  & -0.1185  $\pm$  0.0653 $\pm$ 0.0182 \\ 
  1.842 & 0.215 & 0.135  &  259.6  & -0.2041  $\pm$  0.0430 $\pm$ 0.0195 \\ 
  1.842 & 0.215 & 0.135  &  303.3  & -0.1605  $\pm$  0.0369 $\pm$ 0.0137 \\ 
  1.842 & 0.215 & 0.135  &  337.5  & -0.0493  $\pm$  0.0469 $\pm$ 0.0100 \\ 
  \hline

  2.149 & 0.257 & 0.281  &  21.4   & 0.0356   $\pm$ 0.0400  $\pm$ 0.0131 \\
  2.149 & 0.257 & 0.281  &  60.9   & 0.0927   $\pm$ 0.0454  $\pm$ 0.0125 \\
  2.149 & 0.257 & 0.281  &  95.7   & 0.1488   $\pm$ 0.0510  $\pm$ 0.0338 \\
  2.149 & 0.257 & 0.281  & 139.3   & 0.1112   $\pm$ 0.0732  $\pm$ 0.0178 \\
  2.149 & 0.257 & 0.281  & 183.3   & 0.1052   $\pm$ 0.0933  $\pm$ 0.0298 \\
  2.149 & 0.257 & 0.281  & 222.8   &-0.0744   $\pm$ 0.0760  $\pm$ 0.0183 \\
  2.149 & 0.257 & 0.281  & 259.3   &-0.0912   $\pm$ 0.0549  $\pm$ 0.0253 \\
  2.149 & 0.257 & 0.281  & 302.2   &-0.2004   $\pm$ 0.0390  $\pm$ 0.0248 \\
  2.149 & 0.257 & 0.281  & 337.8   &-0.1041   $\pm$ 0.0468  $\pm$ 0.0171 \\
  \hline

  2.366 & 0.291 & 0.492  &   20.8  &  0.1113  $\pm$ 0.0371  $\pm$ 0.0154 \\
  2.366 & 0.291 & 0.492  &   59.9  &  0.1542  $\pm$ 0.0449  $\pm$ 0.0175 \\
  2.366 & 0.291 & 0.492  &   94.1  &  0.0957  $\pm$ 0.0598  $\pm$ 0.0147 \\
  2.366 & 0.291 & 0.492  &  137.7  & -0.1066  $\pm$ 0.1051  $\pm$ 0.0166 \\
  2.366 & 0.291 & 0.492  &  182.9  &  0.2483  $\pm$ 0.1187  $\pm$ 0.0392 \\
  2.366 & 0.291 & 0.492  &  223.6  & -0.0691  $\pm$ 0.1101  $\pm$ 0.0125 \\
  2.366 & 0.291 & 0.492  &  261.1  & -0.1898  $\pm$ 0.0616  $\pm$ 0.0234 \\
  2.366 & 0.291 & 0.492  &  302.7  & -0.1744  $\pm$ 0.0363  $\pm$ 0.0162 \\
  2.366 & 0.291 & 0.492  &  337.8  & -0.0666  $\pm$ 0.0466  $\pm$ 0.0178 \\
  \hline

  2.447 & 0.312 & 1.089  &  19.7   & 0.0317   $\pm$ 0.0304  $\pm$ 0.0178 \\
  2.447 & 0.312 & 1.089  &  56.7   & 0.0910   $\pm$ 0.0584  $\pm$ 0.0108 \\
  2.447 & 0.312 & 1.089  &  90.6   & 0.1629   $\pm$ 0.1117  $\pm$ 0.0110 \\
  2.447 & 0.312 & 1.089  & 131.2   & 0.0424   $\pm$ 0.3072  $\pm$ 0.0177 \\
  2.447 & 0.312 & 1.089  & 175.3   &-0.9355   $\pm$ 0.3971  $\pm$ 0.0181 \\
  2.447 & 0.312 & 1.089  & 230.5   &-1.1889   $\pm$ 0.5170  $\pm$ 0.0151 \\
  2.447 & 0.312 & 1.089  & 264.3   &-0.0721   $\pm$ 0.1091  $\pm$ 0.0171 \\
  2.447 & 0.312 & 1.089  & 304.8   &-0.1190   $\pm$ 0.0475  $\pm$ 0.0129 \\
  2.447 & 0.312 & 1.089  & 340.5   &-0.0442   $\pm$ 0.0364  $\pm$ 0.0164 \\

 \hline
 \hline
 \end{tabular}
 \caption{Values of the incoherent $A_{LU}$ in $-t$ bins from Fig. \ref{fig:InCohALUphi}.}
 \label{table:InCoh_t_BSA}
 \end{center}
\end{table}
